---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testpkg4

<!-- badges: start -->
<!-- badges: end -->

testpkg4 is my fourth package that aims to collects 
convenient simple functions to solve daily analysis.

## Installation

You can install the development version of testpkg4 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MTRBEKTCBT/testpkg4")
```

## Example

This is a basic example which shows you how to calculate basic 
summary statistics.

```{r example-first}
library(testpkg4)
suppressPackageStartupMessages(library(dplyr))

my_summarise_across(mtcars, am, .vars = mpg)
```

Default argument for `.vars` is `where(is.numeric)`
and second variable is passed to `group_by()`. 
Be careful with that second variable is `...` so you have to explicitly
declare an argument name for third. (`.vars`)

When you want summaries for all of columns in a data frame,
you can just pass the data to first argument.
Then it makes summaries for all of numeric columns.

```{r example-sleep}
my_summarise_across(sleep)
```
